Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-17 WRITEUP/ms.tex
done interferometric cont

% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of co21, co32 emission
%
%
%
%
%
\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
were carried out under the D array configurations of the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 3\,mm
weather conditions and on 2014 February 17 under good 3\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
bandpass calibrators for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

@@

The \ncode{MIRIAD} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25 MHz.

@@

\subsection{\cco Emission} % done
We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
\Fig{co32spec}, which seems to have a double-peak profile.
This is expected if RXJ1131 is truly a disk galaxy (see previous
sections). The high phase noise in the calibration leads to a low SNR
detection. We thus estimate the line intensity to be
35.7$\pm$ 21.9 Jy\,\kms by summing up fluxes over the
linewidth used to infer \bco line intensity ($\sim$700 \kms).

@@

\subsection{Interferometric Continuum}

No continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.
% (consistent with the Gaussian + poly fit to the spectrum continuum level: 2.2 $\pm$ 3.0 mJy).
% line free channels:1, 118, 160, 600
% nchan =(117+600-160+1) = 558
% sigma =  0.83 mJy/B

We detect \pdbi 2\,mm continuum in \Fig{2mm}. The integrated flux density is
1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
centered on the lensing galaxy. A slightly extended emission is seen
also along the lensed arc. This suggests that the detected emission is
toward both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.

We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
in the residual coincides with the lensed arc, and is also consistent with
the difference between the integrated and the peak flux
in the original continuum map ($\sim$0.4 mJy). We therefore adopt this as
emission toward the background galaxy.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
\caption{
An overlay of the 2\,mm continuum emission on the optical image. Contours start at ...
\label{fig:2mm}}
\end{figure}

>>>>

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

\subsection{CARMA \cco} %DONE
Observations of the \cco rotational line ($\nu_{\rm rest}$ = 345.7959899 GHz)
were carried out under the D array configurations of the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) on 2014 February 02 under terrible 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions. The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
bandpass calibrators for both tracks. This results in a total on-source time of 2.94 hours after flagging poor
visibility data.

@@

The \ncode{MIRIAD} package was used to calibrate the visibility data which are
then imaged and deconvolved using the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA = 8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy km s$^{-1}$ beam$^{-1}$
over a channel width of 25 MHz. An rms noise of
$\sigma$ = 0.831 mJy beam\pmOne is reached by averaging over the
line-free channels.

@@

\subsection{\cco Emission} % DONE
We detect resolved \cco line emission toward RXJ1131. The spectrum is shown in
\Fig{co32spec}, which seems to have a double-peak profile.
This is expected if RXJ1131 is truly a disk galaxy (see previous
sections). The high phase noise in the calibration leads to a low SNR
detection. We thus estimate the line intensity to be
35.7$\pm$ 21.9 Jy\,\kms by summing up fluxes over the
linewidth used to infer \bco line intensity ($\sim$700 \kms).

@@

\subsection{Interferometric Continuum} %DONE
No 1.5\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect PdBI 2\,mm continuum in \Fig{2mm}. The integrated flux density is
1.2$\pm$0.2 mJy, with a peak flux $S_\nu$ = 800$\pm$88 \micron Jy\,beam\pmOne
centering on the lensing galaxy. A slightly extended emission is also seen
along the lensed arc. This suggests that the detected emission comes from
both the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in $uv$-plane to remove the unresolved
emission toward the foreground galaxy. The peak flux (0.389$\pm$0.082 mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_\nu$ = 0.39$\pm$0.08 mJy as the 2\,mm continuum emission toward
the background galaxy.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContPdBI.eps}
\caption{
An overlay of the 2\,mm continuum emission on the optical image. Contours start and increment at steps of $\pm$3$\sigma$, where $\sigma$\,=\,0.082 mJy
beam\pmOne. The central cross indicates the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beam is shown in the bottom left corner.
\label{fig:2mm}}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.35\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{
VLA 5\,GHz continuum emission is overlaid on the optical image. Contours start and increment at steps of $\pm$3$\sigma$ of $\sigma$=13\micron Jy beam\pmOne. The beam is shown in the bottom left corner.
 \label{fig:vla}}
\end{figure}

The VLA C-band continuum image in \Fig{vla} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha$\,=\,0.024 for the foreground
galaxy and $\alpha$\,=\,0.345 for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{-\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.
